Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-10-04 packages/spec-haskell/yellowpaper/Paper1.tex
agreement operation output is monoid
adding decaying flow

\part*{Introduction}
%%%%%%%%%%%%%%%%%%%%%%

@@

Other notable extensions used in the paper are: $FunctionalDependencies$, $TypeFamilies$,
$TypeFamilyDependencies$, $GADTs$, $MultiWayIf$.

@@

It should be easy to prove that they satisfy the \textit{axioms A of restricted money distribution}.

>>>>

\part*{Introduction}
%%%%%%%%%%%%%%%%%%%%

@@

Other notable extensions used in the paper are: $FunctionalDependencies$, $TypeFamilies$,
$TypeFamilyDependencies$, $GADTs$.

@@

\paragraph{Decaying Flow}

Another way monetary value could flow is through an exponential decay
function\footnote{\url{https://en.wikipedia.org/wiki/Exponential_decay}.}.

Symbolically, this process can be expressed by the following differential equation, where N is the
quantity and $\lambda$ is a positive rate called the exponential decay constant:

\begin{equation}
    {\displaystyle {\frac {dN}{dt}}=-\lambda N}
\end{equation}

The solution to this equation (see derivation below) is:

\begin{equation}
    {\displaystyle N(t)=N_{0}e^{-\lambda t}}
\end{equation}

But a more convenient semantics of it uses the parameter called ``distribution limit'' ($\theta$)
instead. In this formulation, a decaying flow distributes $\epsilon$ amount of monetary value at a
rate started at $\alpha$ and halving every time period of $\displaystyle \frac{ln(2)}{\lambda}$:

\begin{equation}
    \begin{split}
        [\![decayingFlow\ u_a\ u_b\ \theta\ \lambda\ t']\!] &=
        \lambda u \rightarrow \lambda t \rightarrow \\
        &\begin{cases}
             {\displaystyle  \alpha \cdot e^{-\lambda (t' - t)} - \theta} & (u_a = u) \\
             {\displaystyle -\alpha \cdot e^{-\lambda (t' - t)} + \theta} & (u_b = u) \\
             0 & (otherwise)
        \end{cases}
    \end{split}
\end{equation}

For the simplicity of the later discussion, this form of payment primitive is omitted.
